A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-07-04 manuscript.Rmd
describe example a bit

>>>>

# Preregistration as Code --- an example

At the heart of a PAC lies the planned analysis.
We suggest writing a function that captures the full process of testing a research question beginning from the dataset.
This is a simple example:

```{r planned_analysis}
```

All variables of the dataset except the grouping variable are averaged.
Depending on how skewed the dataset is we apply a rank transformation to the average and then we calculate a t-test with Welch correction in the hope of creating a more robust analysis for non-normal data.
At last the function returns an object with all relevant information.

To use this function one needs a compatible dataset.
At the time of preregistration there is of course no actual data availible.
We therefore simulate a dataset.

```{r simulate_data}
```

We decided to draw non-normal data to test how well our procedure performed under non-optimal situations.
Specifically, we draw from a $\Chi^2$-distribution, where in one group we add difference that conforms to a standardized effect size.
This simulated dataset fits perfectly into our planned analysis:

```{r}
set.seed(112358) # fix state of RNG
simulate_data(n = 400, # n/2 per group
              df = 8, # Chisq with skewness == 1
              d = .2, # Cohen's D
              i = 10) %>% # number of items (should not effect outcome)
  planned_analysis() %>% # `%>%` = output of 1. function becomes argument 2.
  .$test %>% # extract the t.test object
  report::report_text() # use the `report`-package
```
